---
title: "MovieLens Project"
author: "Pongsasit Thongpramoon"
date: "2019年5月12日"
output: pdf_document
---

#1.Introduction

##1.1Introduction
For this project, I created a movie recommendation system using the MovieLens dataset. The version of movielens included in the dslabs package is just a small subset of a much larger dataset with millions of ratings. 
I used the 10M version of the MovieLens dataset, collected by GroupLens Research (https://grouplens.org/datasets/movielens/10m/). 
The target of this project is to train a machine learning algorithm using the inputs of a provided subset to predict movie ratings in the provided validation set.

##1.2 Know the data
## 	1.2.1 Download and Build the dataset.

```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
###################################
# Create edx set and validation set
###################################

# Note: this process could take a couple of minutes

if(!require(tidyverse)) install.packages("tidyverse", repos = "http://cran.us.r-project.org")
if(!require(caret)) install.packages("caret", repos = "http://cran.us.r-project.org")

# MovieLens 10M dataset:
# https://grouplens.org/datasets/movielens/10m/
# http://files.grouplens.org/datasets/movielens/ml-10m.zip

dl <- tempfile()
download.file("http://files.grouplens.org/datasets/movielens/ml-10m.zip", dl)

ratings <- read.table(text = gsub("::", "\t", readLines(unzip(dl, "ml-10M100K/ratings.dat"))),
                      col.names = c("userId", "movieId", "rating", "timestamp"))

movies <- str_split_fixed(readLines(unzip(dl, "ml-10M100K/movies.dat")), "\\::", 3)
colnames(movies) <- c("movieId", "title", "genres")
movies <- as.data.frame(movies) %>% mutate(movieId = as.numeric(levels(movieId))[movieId],
                                           title = as.character(title),
                                           genres = as.character(genres))
movielens <- left_join(ratings, movies, by = "movieId")
```

Split the dataset into 2 subsets, “edX” is train set and “validation” is test set.
```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
# Validation set will be 10% of MovieLens data
set.seed(1)
test_index <- createDataPartition(y = movielens$rating, times = 1, p = 0.1, list = FALSE)
edx <- movielens[-test_index,]
temp <- movielens[test_index,]

# Make sure userId and movieId in validation set are also in edx set
validation <- temp %>% 
     semi_join(edx, by = "movieId") %>%
     semi_join(edx, by = "userId")

# Add rows removed from validation set back into edx set
removed <- anti_join(temp, validation)
edx <- rbind(edx, removed)

rm(dl, ratings, movies, test_index, temp, movielens, removed)
```

I trained my model only on “edX”, “validation” set will be used to test the algorithm.
\pagebreak

##1.2.2	Know Dataset
At first I use head function to see overall data in this dataset.  
```{r head, echo = FALSE}
head(edx) %>% 
  print.data.frame
```

Then find the dimension of edX.
```{r dim, echo = FALSE}
dim(x)
```

Then find the amount of 0 and 3 as given as rating in this dataset.
```{r , echo = FALSE}
#Find zeros were given as ratings in the edx dataset
edx %>% filter(rating == 0) %>% tally()
#Find threes were given as rating in the edx dataset
edx %>% filter(rating == 3) %>% tally()
```

k the movies by movie ratings.

find top five of the rating and show that half stars rating is less than whole star rating. As below.